\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2013-04-11 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex
added FULL_ATTENUATION_SOLID description to the manual

>>>>

\item [{\texttt{FULL\_ATTENUATION\_SOLID}}] Set to \texttt{.true.} to add $Q_\kappa$ attenuation to the simulations in addition to $Q_\mu$
attenuation when the \texttt{ATTENUATION} flag above is on.
Should be off in almost all cases for seismic wave propagation, since $Q_\kappa$ is almost always negligible in Earth models.
However, this parameter can be useful for instance for ocean acoustics simulations, when $Q_\kappa$ is not negligible in the solid
layer at the sea bottom.
